Datasheet for 'Sakura Flowering Dataset

### 2024-12-02 other/datasheet/datasheet_template.qmd
finish !!!

---
title: "Datasheet for 'Sakura Dataset'"
subtitle: ""
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: "D MMMM YYYY"
abstract: "This file recored all the information toward the dataset and usage."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze and model the flowering dates of sakura trees in Japan, focusing on understanding how climatic and geographic factors influence phenology. It addresses the need for a structured, comprehensive dataset combining historical and modern records to study trends related to climate change and its impact on sakura flowering patterns.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset integrates historical data from Prof. Yasuyuki Aono’s work and modern data from the Japan Meteorological Agency (JMA), collected by Alex
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - The temperature are rescraped by Shanjie Jiao, since the origional data provided by Alex existing error in data

>>>>

---
title: "Datasheet for 'Sakura Flowering Dataset'"
subtitle: ""
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: "D MMMM YYYY"
abstract: "This file recored all the information toward the dataset and usage."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @Gebru2021Datasheets.
Dataset are collected by Alex [@Alex2020sakura], which extracted from Dr.Yasuyuki [@yasuyuki2015cherry] and Japan Meteorological Agency [@Japanclimate].
Temperature data are scraped by Shanjie Jiao from Japan Meteorological Agency [@Japanclimate].

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze and model the flowering dates of sakura trees in Japan, focusing on understanding how climatic and geographic factors influence phenology. It addresses the need for a structured, comprehensive dataset combining historical and modern records to study trends related to climate change and its impact on sakura flowering patterns.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset integrates historical data from Prof. Yasuyuki Aono’s work and modern data from the Japan Meteorological Agency [@Japanclimate], collected by Alex
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - The temperature are rescraped by Shanjie Jiao, since the origional data provided by Alex existing error in data
